% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \fcolorbox{black}{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\resdubsubheading}[6]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} & \textit{#6} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Chris C. Ponticello}  & 0434 501 903 (mobile)\\
91 Kilmorey Street &  Christopher.Ponticello@uqconnect.edu.au \\
Carindale, QLD 4152 & http://www.github.com/CPonty \\
\end{tabular*}
\\

\vspace{0.1in}

%\item
%	\ressubheading{}{}{}{}
%	\begin{itemize}
%		\resitem{}
%	\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Villanova College}{Brisbane, QLD}{Grades 5-12}{Jan. 2002 - Nov. 2009}
	\begin{itemize}
		\resitem{Overall Position (OP): 1 (rank 99 equivalent)}
		\resitem{Co-curricular pursuits: orchestra, scouting, video game development}
	\end{itemize}
\item
	\ressubheading{University of Queensland}{Brisbane, QLD}{B.Eng., Computer Systems Engineering}{Feb. 2010 - Present }
	\begin{itemize}
		\resitem{GPA: 5.78/7.00 (cumulative, as of Apr. 2014) }
		\resitem{Graduation: expecting Class IIA Honours (Jul. 2014) }
		\resitem{Relevant topics: Operating System Architecture, Computer Networks, Embedded \& Digital System Design, Control Systems \& Robotics, Artificial Intelligence, System Engineering, Wireless Sensors }
	\end{itemize}
\end{itemize}

\resheading{Awards}
\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\\
		\hspace{5 mm} ICT Excellence Scholarship & 2010\\
		\hspace{5 mm} Dean's Commendation for High Achievement & 2010, 2011\\
		\\
\end{tabular*}

\resheading{University Projects}
\begin{itemize}
\item
	\ressubheading{Recognition and Simulation of Block Diagram System Designs}{}{Engineering Thesis, ENGG4802 \ \textbar \ Supervisor: Dr. Mark Schultz}{Jul. 2013 - Jul. 2014}
	\begin{itemize}
		\resitem{Defined a method for representing engineering system designs using block diagrams on a whiteboard}
		\resitem{Wrote OpenCV computer vision software to capture the design and construct an abstract model}
		\resitem{Wrote modular simulation software capable of using the model to simulate a particular type of system; implemented a prototype for digital logic gates}
	\end{itemize}

\item
	\ressubheading{Horizon Approach Laser Protection SYSTEM | `HAL-P'}{Pair Project}{Wireless Sensor Networks, CSSE4011\ \textbar \ Supervisor: Dr. Matt D'Souza}{Jul. 2013 - Nov. 2013}
	\begin{itemize}
		\resitem{Designed, constructed and programmed indoor, radio-linked sensor network for \\ interdicting airborne targets approaching a position}
		\resitem{Airborne object emits sound waves (filtered, triangulated by microphone sensor nodes) \\ and Infrared pulses (detected, categorized by turret-mounted IR photosensor \& signal demodulator)}
		\resitem{Objects with IR + sonic signature match painted by turret-mounted laser}
		\resitem{Presented design to a panel of WSN researchers at CSIRO's QCAT (Queensland Centre for Advanced Technologies) facility}
	\end{itemize}

\item
	\ressubheading{Ground Vehicle Tracking using Computer Vision | `PringleCV'}{Paid staff role}{Introduction to Embedded Systems, CSSE3010 \ \textbar \ Supervisor: Dr. Matt D'Souza}{Jan. 2014 - Jul. 2014}
	\begin{itemize}
		\resitem{Designed and constructed a programmable tracked rover}
		\resitem{Integrated existing sensor/microcontroller hardware in use by the course}
		\resitem{Wrote computer vision software to track the vehicle from a webcam (position and orientation) }
		\\ \vspace{4 mm} Code: https://github.com/CPonty/PringleCV \ \textbar \ \ Docs: http://goo.gl/Z3D7cc
	\end{itemize}
\end{itemize}

\pagebreak

\resheading{Work Experience}

\begin{itemize}
\item
	\ressubheading{GBST - Global Banking \& Securities Transactions}{Brisbane, QLD}{Intern Developer}{Jan. 2011 - Present}
	\begin{itemize}
		\resitem{Served as part of an agile team developing a large-scale Business Intelligence Reporting solution (BIR)} 
		\resitem{Wrote database queries; designed report generation templates; maintained Java application code}
		\resitem{Wrote documentation; improved workflow automation; created and supported a virtualized development environment}
		\resitem{Trained employees, clients and international contractors on our products, processes and tools}
	\end{itemize}

\item
	\resdubsubheading{UQ ITEE - School of Information Technology and Electrical Engineering}{Brisbane, QLD}{Technology Demonstrator}{Nov. 2012 - Jan. 2013}{}{Jan. 2014 - Present \ \ \ }
	\begin{itemize}
		\resitem{Extended reacTIVision (open-source fiducial tracking software | http://reactivision.sourceforge.net/) with a remote-access, MIDI-based API capable of adjusting device settings on USB webcams. }
		\resitem{Configured a Linux virtual machine with tools \& software libraries required for students of CSSE3010}
		\resitem{Designed and built a wheeled rover + object tracking solution | see `PringleCV' above}
	\end{itemize}
\end{itemize}

%\resheading{Publications}

%\begin{description}
%\item[``Title of paper I authored,"]
%\emph{Proceedings for the conference it was published at} in City, State, 2014.
%\end{description}

\resheading{Skills}
\begin{quote}
\begin{description}
\item[Languages:]
Assembly, Bash Shell, C/C++, Java, Javascript+HTML5, \LaTeX, Python, SPICE, SQL
\item[Software:]
LTSpice, MatLab + Simulink, OpenCV, Postgresql/Microsoft SQL Servers, Git + Svn, TinyOS, FreeRTOS
\item[Operating System:]
Mac OSX, Windows ('95 to current), Linux (Ubuntu +variants; Arch; CentOS)
\item[Electrical:]
Digital/Analog Scopes, Frequency Analyzer, Function Generators, soldering
\item[Miscellaneous:]
	\resitem{Strong troubleshooting and debugging skills}
	\resitem{Comfortable in diverse working environments (unix-based; server-centric; virtualised; embedded platforms; working individually \& within a team)}
		\resitem{3 years' experience in an Agile software development team}
\end{description}
\end{quote}

\resheading{Interests}

\begin{quote}
\begin{description}
\item[Academic:] Computer vision, wireless sensor networks
\item[Membership:] 
	\resitem{Student member of IEEE}
	\resitem{UQ Computing Society executive committee \& founding member (http://uqcs.org.au/)}
\item[Hobbies:] 
	\resitem{Current projects: an Android app (alarm clock, switched off by walking); control system for an automatic bartender (hardware under construction by fellow students).}
	\resitem{Enjoy learning Linux systems; automating tasks via scripting languages; experimenting with hobbyist electronics.}
\end{description}
\end{quote}

\vspace{20 mm}
\rule{550pt}{0.5pt}
Source code for this document: https://github.com/CPonty/latex-resume/blob/master/resume.tex

\end{document}
